---
title: "CleanUpCSVfiles_Script"
author: "Max Strul"
format: html
editor: visual
date: 2023-07-25
---

## Mitochondrial Analyzer Automation

# First we need to clean up the csv files and put all the results into a easily readable results file instead of a bunch of csv files.

To do so run the following code block. Note it will prompt you for the directory, or you can alternatively edit the code with the file directory directly. Please remember to include the full path name. If on mac navigate to your directory using the Finder then in the bottom you can see the visual path where it includes images of folders with names and arrows, then right click and select "Copy File Path".

```{r}
# Load required packages
library(readr)
library(dplyr)

# Prompt user for directory path
dir_path <- readline(prompt = "Enter directory path: ")

# List all CSV files in the directory
csv_files <- list.files(path = dir_path, pattern = "\\.csv$", full.names = TRUE)

# Initialize an empty data frame to store the combined results
combined_data <- data.frame()

# Iterate over each CSV file
for (file in csv_files) {
  # Read the CSV file
  data <- read_csv(file,show_col_types = FALSE)
  
  # Extract the file name without extension
  file_name <- tools::file_path_sans_ext(basename(file))
  
  # Add a new column with the file name to the data
  data_with_name <- data %>% mutate(File = file_name)
  
  # Append the data to the combined results
  combined_data <- bind_rows(combined_data, data_with_name)
}

# Write the combined results to a new CSV file
write_csv(combined_data, file.path(dir_path, "results.csv"))

# Print a message indicating the completion of the process
cat("Data has been successfully combined and saved to 'results.csv'.\n")

#Please double check that each image mask file only has one entry in the combined results.csv - There is a bug in R where the cache is not reset properly and there may be duplicate entries from the same image file.
#The correct way to check is using the "Filename" column and each image mask should only be listed once.

```

```{r}
sessionInfo()
```

## Notes about code

# Written by Max Strul, with the assitance of ChatGPT for error catching & correcting & code optimatzation as well as commentation.
